---
title: "Who does more pushups"
author: "Paul Hamby"
date: "September 18, 2017"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of running and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?


# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->


We are going to run a varaible analysis test and we are also going to use a boxplot, in order to illustrate the data. Once we create the boxplot, were are going to construct a violin plot, in order to see the percentile of weight in corespondence to pushups. Finally, in order to see if our null hypothesis is accurate, we are going to run a t-test and observe what our p-value is.  



# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->

Please see the data below under Graphical Results, Numerical Results, and Inferntial Results. 

## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->
```{r}
myex <-ggplot(pushups,aes(x=position,y=weight))
myex + geom_boxplot()
myex + geom_violin()
```

The plot reveals that line players all weigh more than all but the heaviest skill player. Therefore, we cam generally observe that many of the line players weigh more than the skill players. 

## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=pushups)
```


The line players averaged less pushups than the skill players, at 17 pushups and 50 pushups respectively. It appears the skill players were able to do more pushups then the line players. We can see that by observing the maximium levels of pushups reached by the different poistion groups. The maxmium amount of pushups reached by the skill players were 108, while the maximum amount of pushups reached by the line players was 34. 


# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

We want to run a stats test of difference of means on weight between the skilled and the line players. 

```{r}
t.test(weight~position,data=pushups)
```

The p-value was so low that we conclude that we are going to reject the null hypothesis.The p-value was estimated to be at roughly 1.731e-05 which, is very low. Therefore, the average pushups between the line and skill players are not the same. 

# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->

